Fast and scalable Gaussian process modeling with applications to astronomical time series \vspace{-3\baselineskip}

### 2017-03-14 paper/ms.tex
benchmark plots and captions

\begin{figure}[!htbp]
\begin{center}
\includegraphics[width=\textwidth]{../examples/benchmark/benchmark_darwin.pdf}
\caption{A benchmark showing the computational scaling of the \celerite\
    implementation as a function of the number of data points and the number
    of terms.
    (left) The cost of computing \eq{gp-likelihood}
    \figurelabel{benchmark}}
\end{center}
\end{figure}

\begin{figure}[!htbp]
\begin{center}
\includegraphics[width=\textwidth]{../examples/benchmark/benchmark_darwin_lapack.pdf}
\caption{Benchmark\figurelabel{benchmark-lapack}}
\end{center}
\end{figure}

\begin{figure}[!htbp]
\begin{center}
\includegraphics[width=\textwidth]{../examples/benchmark/benchmark_darwin_sparse.pdf}
\caption{Benchmark\figurelabel{benchmark-sparse}}
\end{center}
\end{figure}

>>>>

\begin{figure}[!htbp]
\begin{center}
\includegraphics[width=\textwidth]{../examples/benchmark/benchmark_darwin.pdf}
\caption{A benchmark showing the computational scaling of \celerite\ with a
    vanilla band solver as a function of the number of data points and the
    number of terms.
    \emph{(left)} The cost of computing \eq{gp-likelihood} with a covariance
    matrix given by \eq{celerite-kernel} as a function of the number of data
    points $N$.
    The different colors show the cost for different numbers of terms $J$ as
    listed in the legend.
    To guide the eye, the black line shows linear scaling in $N$.
    \emph{(right)} The same information plotted as a function of $J$ for
    different values of $N$.
    The legend shows the value of $N$ for each color and the black line shows
    quadratic scaling in $J$.
    \figurelabel{benchmark}}
\end{center}
\end{figure}

\begin{figure}[!htbp]
\begin{center}
\includegraphics[width=\textwidth]{../examples/benchmark/benchmark_darwin_lapack.pdf}
\caption{The same as \Figure{benchmark} but using the band solver from
    \project{LAPACK} with the \project{MKL} \project{BLAS} library.
    \figurelabel{benchmark-lapack}}
\end{center}
\end{figure}

\begin{figure}[!htbp]
\begin{center}
\includegraphics[width=\textwidth]{../examples/benchmark/benchmark_darwin_sparse.pdf}
\caption{The same as \Figure{benchmark} but using the \texttt{SparseLU} solver
    from \project{Eigen} \citep{Guennebaud:2010}.
    \figurelabel{benchmark-sparse}}
\end{center}
\end{figure}
